---
title: "SPC & ITS Analysis App"
format: 
  dashboard:
    scrolling: true
    theme: 
      - spacelab
      - www/custom.scss
    nav-buttons:
      - icon: github
        title: "Source Code"
        href: https://github.com/Rmadillo/SPC_ITS
        target: _blank
logo: images/icon.png
server: shiny
---

```{r}
#| context: setup
#| include: false
#| warning: false
#| message: false

# Load required packages
library(shiny)
library(shinyjs)
library(qicharts2)
library(readxl)
library(dplyr)
library(lubridate)
library(ggplot2)
library(nlme)
library(gtsummary)
library(gt)
library(broom)
library(broom.helpers)
library(tibble)
library(DT)
library(plotly) 
library(AICcmodavg)

# Ensure shinyjs is enabled
useShinyjs()

```

# {.sidebar}

```{r}
#| title: "Configuration"

div(id = "form",
    h4("1. Upload Data"),

    fileInput("file_upload", "Choose CSV or Excel File",
              accept = c(".csv", ".xlsx")),
        
    HTML("<small>Data should be formatted and organized following the guidelines in <a href='[https://doi.org/10.1080/00031305.2017.1375989](https://doi.org/10.1080/00031305.2017.1375989)' target='_blank'>Broman & Woo (2018)</a>.</small>"),
    
    hr(),
    
    h4("2. Configure Chart"),
    # Dynamic UI for variable selection
    uiOutput("variable_selectors"),
    
    selectInput("chart_type", "Select SPC Chart Type:",
                choices = c("Run chart" = "run", 
                            "I chart" = "i", 
                            "I' chart" = "ip",
                            "MR chart" = "mr",
                            "Xbar chart" = "xbar", 
                            "S chart" = "s", 
                            "T chart" = "t",
                            "P chart" = "p", 
                            "P' chart" = "pp",
                            "NP chart" = "np", 
                            "C chart" = "c", 
                            "U chart" = "u",
                            "U' chart" = "up",
                            "G chart" = "g"),
                selected = "run"),
    
    numericInput("multiplier", "Y-Value Multiplier:", value = 1, min = 1),
    
    selectInput("x_period", "Aggregate X-axis by Period:",
                choices = c("None" = "none", 
                            "Seconds" = "sec", 
                            "Minutes" = "min",
                            "Hours" = "hour", 
                            "Days" = "day", 
                            "Weeks" = "week",
                            "Months" = "month", 
                            "Quarters" = "quarter", 
                            "Years" = "year"),
                selected = "none"),
    hr(),
    
    h4("3. Intervention Settings"),
    textInput("intervention_rows", HTML("Intervention Row(s):<br><small> (comma-separated)</small>"),
              placeholder = "e.g., 24, 48"),
    
    radioButtons("intervention_type", "Intervention Effect:",
                 choiceNames = list("None",
                                 HTML("Freeze Baseline<br><small>(uses 1st intervention)</small>"),
                                 HTML("Recalculate<br><small>(uses all interventions)</small>")),
                 choiceValues = list("none", "freeze", "part"),
                 selected = "none"),
    
    textInput("washout_rows", "Washout/Exclude Row(s):",
              placeholder = "e.g., 25, 26, 27"),
    hr(),
    
    h4("4. Plot Customization"),
    
    numericInput("sigfigs", "Decimals (0-5):",
              value = 2, min = 0, max = 5),
    
    checkboxInput("y_neg_check", "Positive Y-axis only?", value = FALSE),
    
    # New Goal Line Input
    numericInput("goal_value", "Goal Line (Y-axis):", value = NULL),
    
    uiOutput("plot_labels_ui")
)

hr()
actionButton("run_analysis", "Run Analysis", icon = icon("play"), class = "btn-primary")
br()
actionButton("reset_app", "Start Over", icon = icon("sync-alt"), class = "btn-danger")
hr()

```

{width=100%}

<hr>

# Data Preview

```{r}
DT::dataTableOutput("data_table")

```

# SPC Analysis

## Row {height="600px"}

### SPC Chart

```{r}
plotlyOutput("spc_plot", height = "100%") 

```

## Row {height="auto"}

### Downloads

```{r}
div(style = "display: flex; gap: 10px; align-items: center;",
    downloadButton("download_plot", "Download SPC Plot (PNG, 600dpi)"),
    downloadButton("download_data", "Download SPC Results (CSV)")
)

```

# ITS Analysis

## Row {height="600px"}

### Interrupted Time Series Analysis

```{r}
plotlyOutput("its_plot", height = "100%")

```

## Row {height="auto"}

### Download ITS Results

```{r}
div(style = "display: flex; gap: 10px; align-items: center;",
    downloadButton("download_its_plot", "Download ITS Plot (PNG, 600dpi)"),
    downloadButton("download_its_data", "Download ITS Results (CSV)")
)

```

## Row {height="auto"}

### ITS Model Results

```{r}
gt_output("its_summary_table")

```

## Row {height="auto"}

### Selected Best Fit Model Summary

```{r}
verbatimTextOutput("its_model_summary")

```

# About

#### About this Application

This tool provides **Statistical Process Control (SPC)** and **Interrupted Time Series (ITS)** analysis capabilities.

**How to use:**

1. **Upload Data:** Upload a CSV or Excel file. If it's an Excel file, make sure the first sheet in the workbook contains your data for analysis.
2. **Configure:** Select your Date and Value columns in the sidebar.
3. **Intervention:** Specify the row numbers where interventions occurred. You can look at the *Data Preview* to see on which row(s) the interventions occur.
4. **Run:** Click "Run Analysis" to generate analysis results. You can then click on the SPC or ITS links in the top navbar to see those results.

#### Tips for Organizing Your Data {#data-organization}

**Tips for Organizing Your Data for Analysis:**

* **Be consistent**
* Consistent codes for categorical variables (plain text is fine).
* Consistent fixed code for any missing values (eg, NA).
* Consistent variable names.
* Consistent subject identifiers.
* Consistent data layout in multiple files.
* Be careful about extra spaces within cells.


* **Choose good names for things**
* Choose short, unique, and meaningful names.
* Avoid spaces in variable names, they make programming harder.


* **Write dates as YYYY-MM-DD**
* **No empty cells (unless they are *explicitly* meant to be read as *NA*)**
* It is common for cells to be left blank when a single value was meant to be repeated multiple times. Please do not do this! It is additional work for the analyst to determine the implicit values for these cells.
* Do not merge cells.


* **Put just one thing in a cell**
* **Make it a rectangle**
* Single big rectangle with *rows corresponding to subjects* and *columns corresponding to variables*.
* The first row should contain variable names.
* Do not use more than one row for the variable names.
* If there is no reasonable way to create a single rectangle, you may need additional sheets.


* **Create a data dictionary**
* **No calculations in the raw data file**
* **Do not use font color or highlighting as data**
* Create indicator variables instead of using color.


* **Make backups**
* Keep an original version in a secure location!


* **Use data validation to avoid errors**
* **Save a copy in a plain text file (e.g., .csv)**

**Source:** Karl W. Broman & Kara H. Woo. 2018. Data Organization in Spreadsheets. *The American Statistician*, 72(1):2-10. DOI: <a href="https://doi.org/10.1080/00031305.2017.1375989"  target="_blank">10.1080/00031305.2017.1375989</a>.

#### Contact

Clinical Analytics & Center for Quality and Patient Safety



Seattle Children's Hospital

Version: 0.9. *This app was published on January 23, 2025.*

```{r}
#| context: server

#-- Reactive Value for Storing Data and Plots --#
rv <- reactiveValues(
    data = NULL,
    spc_plot = NULL,      # Stores ggplot object for downloading
    spc_plot_ly = NULL,   # Stores plotly object for rendering
    spc_plot_data = NULL, # Stores data frame with SPC results for downloading
    its_plot = NULL,      # Stores ggplot object for downloading
    its_plot_ly = NULL,   # Stores plotly object for rendering
    its_data = NULL,      # Stores data frame with predictions for downloading
    its_model_summary = NULL,
    its_summary_table = NULL
)

#-- Link Logic: Switch Tab and Scroll --#
observeEvent(input$link_broman, {
    runjs("
      var navLinks = document.querySelectorAll('.navbar-nav a');
      for (var i = 0; i < navLinks.length; i++) {
        if (navLinks[i].textContent.trim() === 'About') {
          navLinks[i].click();
          setTimeout(function() {
             var section = document.getElementById('data-organization');
             if(section) section.scrollIntoView({behavior: 'smooth'});
          }, 300); 
          break;
        }
      }
    ")
})

#-- 1. Data Loading --#
observeEvent(input$file_upload, {
    req(input$file_upload)
    file_path <- input$file_upload$datapath
    
    if (endsWith(file_path, ".csv")) {
        df <- read.csv(file_path, stringsAsFactors = FALSE)
    } else if (endsWith(file_path, ".xlsx")) {
        df <- readxl::read_excel(file_path)
    } else {
        showNotification("Unsupported file type.", type = "error")
        return(NULL)
    }
    
    rv$data <- df
    # Reset results on new upload
    rv$spc_plot <- NULL
    rv$spc_plot_ly <- NULL
    rv$spc_plot_data <- NULL
    rv$its_plot <- NULL
    rv$its_plot_ly <- NULL
    rv$its_data <- NULL
    rv$its_model_summary <- NULL
    rv$its_summary_table <- NULL
})

#-- 2. Dynamic UI Generation --#
output$variable_selectors <- renderUI({
    req(rv$data)
    col_names <- names(rv$data)
    # Attempt to guess date column
    date_col_guess <- col_names[sapply(rv$data, function(col) inherits(col, c("Date", "POSIXt")))]
    if(length(date_col_guess) == 0) {
        date_col_guess <- grep("date", col_names, ignore.case = TRUE, value = TRUE)[1]
    }
    
    tagList(
        selectInput("date_var", "Date (X) Variable:", choices = col_names, selected = date_col_guess),
        selectInput("y_var", "Value (Y) Variable:", choices = col_names[sapply(rv$data, is.numeric)], selected = col_names[sapply(rv$data, is.numeric)][1]),
        selectInput("n_var", "Subgroup Size (n) (Optional):", choices = c("None", col_names[sapply(rv$data, is.numeric)]))
    )
})

output$plot_labels_ui <- renderUI({
    req(input$y_var, input$date_var)
    tagList(
        textInput("xlab_text", "X-axis Label:", value = input$date_var),
        textInput("ylab_text", "Y-axis Label:", value = input$y_var),
        textInput("title_text", "Plot Title:", value = paste("Analysis of", input$y_var))
    )
})

#-- 3. Data Prep --#
prepared_data <- reactive({
    req(rv$data, input$date_var, input$y_var)
    df <- rv$data
    
    df[[input$y_var]] <- as.numeric(df[[input$y_var]])
    df[[input$date_var]] <- as.Date(df[[input$date_var]])
    
    if(any(is.na(df[[input$date_var]]))) {
        showNotification("Warning: Rows with missing dates removed.", type = "warning")
    }
    df %>% 
        filter(!is.na(.data[[input$date_var]]), !is.na(.data[[input$y_var]])) %>%
        arrange(.data[[input$date_var]])
})

#-- 4. Main Analysis Logic --#
observeEvent(input$run_analysis, {
    req(prepared_data(), input$y_var, input$date_var)
    
    df <- prepared_data()
    if (nrow(df) == 0) return()
    
    # Process Intervention Rows
    intervention_points <- NULL
    if (nchar(input$intervention_rows) > 0) {
        tryCatch({
            intervention_points <- as.numeric(unlist(strsplit(input$intervention_rows, ",")))
            intervention_points <- intervention_points[!is.na(intervention_points)]
        }, error = function(e) showNotification("Invalid intervention rows.", type = "error"))
    }
    
    # Process Washout Rows
    exclude_arg <- NULL
    if (nchar(input$washout_rows) > 0) {
        tryCatch({
            exclude_arg <- as.numeric(unlist(strsplit(input$washout_rows, ",")))
            exclude_arg <- exclude_arg[!is.na(exclude_arg)]
        }, error = function(e) showNotification("Invalid washout rows.", type = "error"))
    }
    
    # === SPC Analysis ===
    freeze_arg <- if (input$intervention_type == "freeze" && !is.null(intervention_points)) intervention_points[1] else NULL
    part_arg <- if (input$intervention_type == "part" && !is.null(intervention_points)) intervention_points else NULL
    
    charts_using_index <- c('mr', 'g', 't')
    
    x_period_arg <- if (!(input$chart_type %in% charts_using_index) &&
                        !is.null(input$x_period) && input$x_period != "none") {
        tolower(input$x_period)
    } else { NULL }
    
    y_arg <- df[[input$y_var]]
    n_arg <- if (!is.null(input$n_var) && input$n_var != "None") df[[input$n_var]] else NULL
    
    x_arg <- if (input$chart_type %in% charts_using_index) seq_len(nrow(df)) else df[[input$date_var]]

    spc_result <- tryCatch({
        qic(x = x_arg, y = y_arg, n = n_arg, 
            chart = input$chart_type, x.period = x_period_arg,
            freeze = freeze_arg, part = part_arg, exclude = exclude_arg,
            multiply = input$multiplier, y.neg = !input$y_neg_check,
            title = input$title_text, ylab = input$ylab_text, xlab = input$xlab_text,
            show.grid = TRUE)
    }, error = function(e) {
        showNotification(paste("SPC Error:", e$message), type = "error")
        NULL
    })
    
    if(!is.null(spc_result)) {
        rv$spc_plot_data <- spc_result$data 
        spc_data <- spc_result$data
        
        # Manually blank out lines/limits for excluded (washout) points
        if(!is.null(exclude_arg) && length(exclude_arg) > 0) {
             valid_exclude <- exclude_arg[exclude_arg <= nrow(spc_data)]
             if(length(valid_exclude) > 0) {
               spc_data$cl[valid_exclude] <- NA
               spc_data$ucl[valid_exclude] <- NA
               spc_data$lcl[valid_exclude] <- NA
             }
        }

        # Build hover text & grouping var for breaks
        spc_data <- spc_data %>%
            mutate(
                point_hover = paste0(
                    input$xlab_text, ": ", x, "<br>",
                    input$ylab_text, ": ", round(y, input$sigfigs)
                ),
                cl_hover = paste0("Centerline: ", round(cl, input$sigfigs)),
                ucl_hover = paste0("Upper Control Limit: ", round(ucl, input$sigfigs)),
                lcl_hover = paste0("Lower Control Limit: ", round(lcl, input$sigfigs)),
                cl_group = cumsum(c(0, abs(diff(coalesce(cl, 0))) > 1e-6))
            )
        
        # Base Plot
        p <- ggplot(spc_data, aes(x = x))
        
        # 0. Goal Line (First Layer, if exists)
        if (!is.na(input$goal_value) && !is.null(input$goal_value)) {
            p <- p + geom_hline(yintercept = input$goal_value, 
                                linetype = "dotted", color = "darkgreen", linewidth = 0.5)
        }
        
        # 1. Intervention Lines (Bottom Layer)
        if (!is.null(intervention_points) && length(intervention_points) > 0) {
            p <- p + geom_vline(xintercept = as.numeric(spc_data$x[intervention_points]),
                                linetype = "dotted", color = "darkblue")
        }
        
        # 2. Shading (Ribbon)
        p <- p + geom_ribbon(aes(ymin = lcl, ymax = ucl, group = cl_group), alpha = 0.2, fill = "gray")
        
        # 3. Centerline (Visible)
        p <- p + geom_line(aes(y = cl, group = cl_group), color = "black")
        
        # 4. Data Lines and Points
        p <- p + geom_line(aes(y = y), color = "#5DA5DA") + 
                 geom_point(aes(y = y, color = sigma.signal)) +
                 geom_point(data = spc_data[exclude_arg,], aes(y = y), color = "#C8C8C8") +
                 scale_color_manual(values = c("FALSE" = "#5DA5DA", "TRUE" = "#FAA43A"), guide = "none")
        
        # 5. Invisible Layers for Hover Text (alpha=0 makes them invisible but reactive)
        p <- p + geom_point(aes(y = y, text = point_hover), alpha = 0) +
                 geom_line(aes(y = cl, text = cl_hover, group = cl_group), alpha = 0) +
                 geom_line(aes(y = ucl, text = ucl_hover, group = cl_group), alpha = 0) +
                 geom_line(aes(y = lcl, text = lcl_hover, group = cl_group), alpha = 0)
        
        # Labels and Theme
        p <- p + labs(
            title = input$title_text,
            x = input$xlab_text,
            y = input$ylab_text
        ) + theme_bw() +
            theme(legend.position = "none") 

        rv$spc_plot <- p
        # Use tooltip="text" to ONLY show the custom 'text' aesthetic
        rv$spc_plot_ly <- ggplotly(p, tooltip = "text")
    }
    
    # === ITS Analysis ===
    if (!is.null(rv$spc_plot_data) && !is.null(intervention_points) && length(intervention_points) > 0) {
        df_for_its <- rv$spc_plot_data
        df_for_its$time <- seq_len(nrow(df_for_its))
        
        # Create Level and Trend variables
        level_vars <- c()
        trend_vars <- c()
        for (i in seq_along(intervention_points)) {
            int_point <- intervention_points[i]
            level_name <- paste0("level_", i)
            trend_name <- paste0("trend_", i)
            
            df_for_its[[level_name]] <- ifelse(df_for_its$time >= int_point, 1, 0)
            df_for_its[[trend_name]] <- c(rep(0, int_point - 1), seq_len(nrow(df_for_its) - int_point + 1)) * df_for_its[[level_name]]
            
            level_vars <- c(level_vars, level_name)
            trend_vars <- c(trend_vars, trend_name)
        }
        
        # Exclude washout
        df_for_its$excluded <- FALSE
        if(!is.null(exclude_arg) && length(exclude_arg) > 0) df_for_its$excluded[exclude_arg] <- TRUE
        df_model_its <- df_for_its[!df_for_its$excluded, ]
        
        # Build formulas
        formula_full_str <- paste("y ~ time +", paste(c(level_vars, trend_vars), collapse = " + "))
        formula_level_only_str <- paste("y ~ time +", paste(level_vars, collapse = " + "))
        
        # Fit models
        model_full <- tryCatch(gls(as.formula(formula_full_str), data = df_model_its, correlation = corARMA(p = 1, q = 0), method = "ML", na.action = na.omit), error = function(e) NULL)
        model_level_only <- tryCatch(gls(as.formula(formula_level_only_str), data = df_model_its, correlation = corARMA(p = 1, q = 0), method = "ML", na.action = na.omit), error = function(e) NULL)
        
        if (!is.null(model_full) && !is.null(model_level_only)) {
            # Compare AIC
            if (AIC(model_full) < AIC(model_level_only)) {
                best_model <- model_full
                model_name <- "Full Model with Trend"
            } else {
                best_model <- model_level_only
                model_name <- "Level-Change Model"
            }
            
            rv$its_model_summary <- c(
                paste("Selected Best Fit:", model_name),
                capture.output(summary(best_model))
            )
            
            # Summary Table (Manual Extraction for gls objects - bypassing broom)
            rv$its_summary_table <- tryCatch({
                # Extract coefficients table directly from model summary
                summ <- summary(best_model)
                coef_mat <- summ$tTable
                
                # Approximate 95% CI (coef +/- 1.96 * SE)
                est <- coef_mat[, "Value"]
                se <- coef_mat[, "Std.Error"]
                lower <- est - (1.96 * se)
                upper <- est + (1.96 * se)
                
                # Create tidy-like data frame manually
                tidy_model <- data.frame(
                    term = rownames(coef_mat),
                    estimate = est,
                    std.error = se,
                    statistic = coef_mat[, "t-value"],
                    p.value = coef_mat[, "p-value"],
                    conf.low = lower,
                    conf.high = upper,
                    stringsAsFactors = FALSE
                )
                
                # Render table with gt
                tidy_model %>%
                  mutate(p.value = format.pval(p.value, digits = 2, eps = 0.001)) %>%
                  select(term, estimate, std.error, statistic, p.value, conf.low, conf.high) %>%
                  gt() %>%
                  fmt_number(columns = c(estimate, std.error, statistic, conf.low, conf.high), decimals = 3) %>%
                  tab_header(title = "ITS Model Results")
            }, error = function(e) {
                tibble(Error = paste("Table generation failed:", e$message)) %>% gt()
            })
            
            # Predictions
            preds_se <- tryCatch({
                AICcmodavg::predictSE.gls(best_model, newdata = df_for_its, se.fit = TRUE)
            }, error = function(e) {
                list(fit = predict(best_model, newdata = df_for_its), se.fit = rep(0, nrow(df_for_its)))
            })
            
            df_for_its$pred <- preds_se$fit
            df_for_its$se <- preds_se$se.fit
            df_for_its$lower_ci <- df_for_its$pred - (1.96 * df_for_its$se)
            df_for_its$upper_ci <- df_for_its$pred + (1.96 * df_for_its$se)
            
            # Counterfactual
            df_counterfactual <- df_for_its
            for(var in c(level_vars, trend_vars)) if(var %in% names(df_counterfactual)) df_counterfactual[[var]] <- 0
            df_for_its$counterfactual <- predict(best_model, newdata = df_counterfactual)

            # Clean Washout Data
            df_for_its$pred[df_for_its$excluded] <- NA
            df_for_its$lower_ci[df_for_its$excluded] <- NA
            df_for_its$upper_ci[df_for_its$excluded] <- NA
            
            # Save Data for Download
            rv$its_data <- df_for_its

            # Segment ID for Ribbons
            df_for_its$segment_id <- cumsum(c(0, abs(diff(as.integer(df_for_its$excluded)))))

            # Hover Text
            df_for_its$point_hover <- paste0(
                input$xlab_text, ": ", df_for_its$x, "<br>",
                input$ylab_text, ": ", round(df_for_its$y, input$sigfigs)
            )
            df_for_its$pred_hover <- paste0("Model Fit: ", round(df_for_its$pred, input$sigfigs))
            df_for_its$cf_hover <- paste0("Counterfactual: ", round(df_for_its$counterfactual, input$sigfigs))
            df_for_its$ucl_hover <- paste0("Upper Confidence Limit: ", round(df_for_its$upper_ci, input$sigfigs))
            df_for_its$lcl_hover <- paste0("Lower Confidence Limit: ", round(df_for_its$lower_ci, input$sigfigs))
            
            # Plot
            its_plot_obj <- ggplot(df_for_its, aes(x = x, y = y)) 
            
            # 0. Goal Line (First Layer)
            if (!is.na(input$goal_value) && !is.null(input$goal_value)) {
                its_plot_obj <- its_plot_obj + 
                    geom_hline(yintercept = input$goal_value, 
                               linetype = "dotted", color = "darkgreen", linewidth = 0.5)
            }
                
            its_plot_obj <- its_plot_obj + 
                geom_vline(xintercept = as.numeric(df_for_its$x[intervention_points]), 
                           linetype = "dotted", color = "darkblue") +
                
                geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, group = segment_id), 
                            alpha = 0.2, fill = "#8C8C8C") +
                
                geom_line(data = subset(df_for_its, !excluded), color = "#5DA5DA") +
                
                geom_point(aes(color = excluded)) +
                scale_color_manual(values = c("FALSE" = "#5DA5DA", "TRUE" = "#C8C8C8"), guide = "none") +
                
                geom_line(aes(y = pred, group = 1), color = "#8C8C8C", linewidth = 1) +
                geom_line(data = subset(df_for_its, time >= min(intervention_points)), 
                          aes(y = counterfactual, group = 1), 
                          color = "blue", linetype = "dashed", linewidth = 0.8) +
                
                # Invisible Layers for Tooltips
                geom_point(aes(text = point_hover), alpha = 0) +
                geom_line(aes(y = pred, text = pred_hover, group = 1), alpha = 0) +
                geom_line(data = subset(df_for_its, time >= min(intervention_points)), 
                          aes(y = counterfactual, text = cf_hover, group = 1), alpha = 0) +
                geom_line(aes(y = upper_ci, text = ucl_hover, group = segment_id), alpha = 0) +
                geom_line(aes(y = lower_ci, text = lcl_hover, group = segment_id), alpha = 0) +
                
                labs(title = paste("ITS Analysis for", input$y_var), subtitle = model_name, x = input$xlab_text, y = input$ylab_text) +
                theme_bw() +
                theme(legend.position = "none")
            
            rv$its_plot <- its_plot_obj
            rv$its_plot_ly <- ggplotly(its_plot_obj, tooltip = "text")
            
        } else {
            rv$its_model_summary <- "ITS model fitting failed."
        }
    } else {
        rv$its_plot <- NULL
        rv$its_plot_ly <- NULL
        rv$its_model_summary <- NULL
    }
})

#-- 5. Outputs --#
output$spc_plot <- renderPlotly({
    req(rv$spc_plot_ly)
    rv$spc_plot_ly
})

output$its_plot <- renderPlotly({
    req(rv$its_plot_ly)
    rv$its_plot_ly
})

output$its_summary_table <- render_gt({
    req(rv$its_summary_table)
    rv$its_summary_table
})

output$its_model_summary <- renderPrint({
    req(rv$its_model_summary)
    cat(rv$its_model_summary, sep = "\n")
})

output$data_table <- DT::renderDataTable({
    req(prepared_data())
    DT::datatable(prepared_data(), filter = "top", options = list(pageLength = 10, scrollX = TRUE))
})

#-- 6. Reset Logic --#
observeEvent(input$reset_app, {
    shinyjs::reset("form")
    rv$data <- NULL
    rv$spc_plot <- NULL
    rv$spc_plot_ly <- NULL
    rv$its_plot <- NULL
    rv$its_plot_ly <- NULL
    rv$its_data <- NULL
    rv$its_model_summary <- NULL
    showNotification("App reset.", type = "message")
})

#-- 7. Downloads --#
output$download_plot <- downloadHandler(
    filename = function() { paste0("spc-chart-", Sys.Date(), ".png") },
    content = function(file) {
        req(rv$spc_plot)
        ggsave(file, plot = rv$spc_plot, device = "png", width = 6.5, height = 5, dpi = 600)
    }
)

output$download_its_plot <- downloadHandler(
    filename = function() { paste0("its-plot-", Sys.Date(), ".png") },
    content = function(file) {
        req(rv$its_plot)
        ggsave(file, plot = rv$its_plot, device = "png", width = 6.5, height = 5, dpi = 600)
    }
)

output$download_its_data <- downloadHandler(
    filename = function() { paste0("its-data-", Sys.Date(), ".csv") },
    content = function(file) {
        req(rv$its_data)
        write.csv(rv$its_data, file, row.names = FALSE)
    }
)

output$download_data <- downloadHandler(
    filename = function() { paste0("spc-data-", Sys.Date(), ".csv") },
    content = function(file) {
        req(rv$spc_plot_data)
        write.csv(rv$spc_plot_data, file, row.names = FALSE)
    }
)

```